A Plasma Torus Around a Young Low-Mass Star

### 2025-03-12 paper/ms.tex
update ms

Spec. Type\dotfill                      & Spectral Type\dotfill                                          & MXV              & 4 \\ % TODO TODO

@@

$a_1$\dotfill                           & Clump 1 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.1-2.7         & X \\
$a_2$\dotfill                           & Clump 2 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  3.9             & X \\

@@

{\it Effective temperature, radius, and mass}
For the stellar effective temperature and radius, we adopted the results
from the spectral energy distribution fitting methods described by
\cite{Bouma2024}.
In brief, this approach used \texttt{astroARIADNE} \cite{Vines2022} with
the BT-Settl stellar atmosphere models \cite{Allard2012}, assuming the
\cite{Asplund2009} solar abundances, and the \cite{Barber2006} water
line lists.  
This routine fitted for the stellar effective temperature, radius,
reddening, surface gravity, metallicity, and distance by comparing the
measured broadband magnitudes against pre-computed model grids.
Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
2MASS, SDSS, and WISE $W1$ and $W2$.
This method has the best constraining power for the star's effective
temperature and radius; the surface gravity, metallicity, and reddening
are typically only weakly constrained.
Given the effective temperature, stellar radius, and previously
determined age, we then estimated the stellar mass by interpolating
against the PARSEC v1.2S isochrones \cite{Chen2014}. 
Specifically, we used the distance metric defined in Equation~8 of
\cite{Bouma2024}, in order to select the model mass closest to the
observed temperature, radius, and age.  We derived the uncertainty in
the mass based by propagating the statistical uncertainties in each of
these parameters.

>>>>

Spec. Type\dotfill                      & Spectral Type\dotfill                                          & M5.5Ve           & 4 \\

@@

$a_1$\dotfill                           & Clump 1 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.1-2.7         & 4 \\
$a_2$\dotfill                           & Clump 2 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  3.9             & 4 \\

@@

{\it Effective temperature, radius, mass, and spectral type}
For the stellar effective temperature and radius, we adopted the results
from the spectral energy distribution fits described by
\cite{Bouma2024}.  To summarize, this approach used
\texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
solar abundances and the \cite{Barber2006} water line lists.  This
approach fitted for the stellar effective temperature, radius,
reddening, surface gravity, metallicity, and distance by comparing the
measured broadband magnitudes against pre-computed model grids.
Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
2MASS, SDSS, and WISE $W1$ and $W2$.  This method has the most
constraining power for the star's effective temperature (2972 $\pm$
40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
metallicity, and reddening are typically only weakly constrained.  We
determined the star's spectral type to be M5.5Ve by visually comparing
against the photometric standards presented by \cite{Bochanski2007};
this qualitatively agrees with the effective temperature from the SED
fitting \cite{Pecaut2013}.  With the effective temperature, stellar
radius, and previously determined age, we then estimated the stellar
mass by interpolating against the PARSEC v1.2S isochrones
\cite{Chen2014}.  Specifically, we used the distance metric defined in
Equation~8 of \cite{Bouma2024} to select the model mass closest to the
observed temperature, radius, and age.  We derived the uncertainty in
the mass based by propagating the statistical uncertainties in each of
these parameters.
